---
title: "Lab 3"
author: "Jen McGregor"
date: "10/8/2021"
output:
  prettydoc::html_pretty:
  theme: hpstr
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(english)
library(glue)
library(purrr)
```

**The song [“12 Days of Christmas”](https://en.wikipedia.org/wiki/The_Twelve_Days_of_Christmas_(song)), written around 1780, tells the tale of many gifts a person receives in the days leading up to Christmas.**

**These gifts repeat and compound; on the first day, the narrator recieves: A partridge in a pear tree. On the last day, he or she receives: Twelve Drummers Drumming, Eleven Pipers Piping, Ten Lords a Leaping, Nine Ladies Waiting, Eight Maids a Milking, Seven Swans a Swimming, Six Geese a Laying, Five Golden Rings, Four Calling Birds, Three French Hens, Two Turtle Doves, And a Partridge in a Pear Tree.**

**Your task will be to write functions and loop over them to sing the whole song.**

## A Test Dataset

**Run the code below to load a dataset called xmas that contains the crucial information about the gifts in the song. We will use this dataset to test out our functions as we work on them.**

```{r}
xmas <- read.csv("https://www.dropbox.com/s/12ipnczn0fygglt/xmas.csv?dl=1")
```

# Step One: Make gift phrases

**Write a function called make_phrase that takes as input the necessary information, and returns a phrase.**

```{r}
make_phrase <- function(num,gift)
  {numword <- english(num)
  glue("{numword} {gift}")
  }

make_phrase(10, "lords a-leaping")

```
**Try your function out on the xmas data, by making a new variable containing the daily phrases.**

```{r}
xmas %>%
 mutate(GiftPhrase=pmap_chr(xmas,~make_phrase(..1,..3)))

```

# Step Two: Verses

**Write a function called sing_verse that takes as input:**
  
  **1. A number indicating which day to sing about**
  
  **2. A vector that contains the day labels, like “first”, “second” etc.**
  
  **3. A vector that contains the gift for each day.**

```{r}
sing_verse <- function(num,daywords,gifts){
  subverse <- map_chr(num:1,~make_phrase(.x,gifts[.x]))
  head <- paste(
    "On the", daywords[num],
    "day of Christmas my true love sent to me,"
  )
  verse <- append(head,subverse,1)
  verse <- verse %>% paste(collapse = "\n")
  return(verse)
}

sing_verse(2, xmas$Day.in.Words, xmas$Gift.Item)
sing_verse(7, xmas$Day.in.Words, xmas$Gift.Item)
sing_verse(11, xmas$Day.in.Words, xmas$Gift.Item)
```

# Step Three: Sing the whole song.


**Write a function called sing_xmas_song() that takes as input:**

  **1. A vector of day numbers (1, 2, 3, ...)**

  **2. A vector of day names (first, second, …)**

  **3. A vector of gifts**

**And returns the whole text of the song, for all 12 verses. This step will require you to use iteration in some way.**

```{r}
sing_xmas_song <- function(num,daynames,gifts){
  song <- map_chr(num,~sing_verse(.x,daynames,gifts)) %>%
    paste(collapse = "\n")
  return(song)
}

sing_xmas_song(xmas$Day,xmas$Day.in.Words,xmas$Gift.Item)%>%
  cat()
```


# Step Four: Try your functions
**Use the following code to load a dataset that is different from the original xmas song. Note that the column names of this dataset are not the same as they were for the original xmas data!**

**Use the function sing_xmas_song() with this dataset to sing a new version of “12 Days of Christmas”.**

```{r}
xmas2 <- read.csv("https://www.dropbox.com/s/tmilnd6ad8k26wy/xmas2.csv?dl=1")
sing_xmas_song(xmas2$Day,xmas2$Day.in.Words,xmas2$Gift.Item)%>%
  cat()
```